---
output: pdf_document
---
---
title: "Final Project"
author: "Melanie Thompson"
date: "December 12, 2015"
output: pdf_document
---
```{r}
#Clear out your environment.
rm(list=ls())
#load libraries 

library(lubridate)
library(foreign)
library(WDI)
library(countrycode)
library(gdata)
library(zoo)
library(date)
library(ggplot2)
library(Hmisc)
library(stargazer)

```
```{r}
# Loading my data
# Set your working directory to wherever you have saved this data.
setwd("/Users/Mlthomps/Dropbox/Coup Dataset")
OrigData <- read.csv("Mycoupdataset.12.11.15.csv", header=TRUE)
```
First, we need to fix the year formatting, as it is not in a workable R format.
```{r}
# Converting date columns into correct formats as dates.
OrigData$CoupStart <- as.Date(OrigData$date.of.coup, format = "%m/%d/%y")
OrigData$CoupEnd <- as.Date(OrigData$ExitDate, format = "%m/%d/%y")
OrigData$ElectionDate <- as.Date(OrigData$Date.of.Election...Round.one, format = "%m/%d/%y")
# Correct invalid years (the package sometimes changes years into years that have not happened yet. Most of these occur in the 60's and are incorrectly changed to 2060, not 1960)

OrigData$CoupStart[5] <- "1966-01-03"
OrigData$CoupStart[6] <- "1966-01-03"
OrigData$CoupStart[29] <- "1968-08-01"
OrigData$CoupEnd[29] <- "1968-08-01"
OrigData$CoupStart[64] <- "1962-12-17"
OrigData$CoupEnd[64] <- "1962-12-17"

# Get rid of old date columns
OrigData$date.of.coup <- NULL
OrigData$ExitDate <- NULL
OrigData$Date.of.Election...Round.one <- NULL

#Extract Year - this wil be important for merging later!
OrigData$Coupyear <- format(OrigData$CoupStart, "%Y")
OrigData$Exityear <- format(OrigData$CoupEnd, "%Y")
OrigData$Electionyear <- format(OrigData$ElectionDate, "%Y")
```
Now we can calculate the Reign (time in power) of the Coup Leader
```{r}
OrigData$Reign.days<- difftime(OrigData$CoupEnd,OrigData$CoupStart, units = c("days"))
OrigData$Reign.weeks<- difftime(OrigData$CoupEnd,OrigData$CoupStart, units = c("weeks"))
OrigData$Reign.years <- year(OrigData$CoupEnd)-year(OrigData$CoupStart)
```

How long from the end of the coup to the election?

```{r}
# Calculating years from coup to election
OrigData$TimeOff.days<- difftime(OrigData$ElectionDate,OrigData$CoupEnd, units = c("days"))
OrigData$TimeOff.weeks<- difftime(OrigData$ElectionDate,OrigData$CoupEnd, units = c("weeks"))
OrigData$TimeOff.years <- year(OrigData$ElectionDate)- year(OrigData$CoupEnd)
```
Assigning a Country Code
```{r}
OrigData$cown <- countrycode(OrigData$Country, "country.name", "cown")
```
Merging World Bank Data: GDP CoupStart
```{r}
#download data
wdi.gdp <- WDI(country = "all", indicator = c("NY.GDP.PCAP.CD"), start = 1960, end = 2015) 
# Add "iso2c" column in OrigData
OrigData$iso2c <- countrycode(OrigData$Country, "country.name", "iso2c")
# Need to rename Country to match WDI year. Lesson: Never capitalize when making your own dataset.
colnames(OrigData)[colnames(OrigData)=="Country"] <- "country"
colnames(wdi.gdp)[colnames(wdi.gdp)=="year"] <- "Coupyear"
OrigData <- merge(OrigData,wdi.gdp,by=c("Coupyear","iso2c"),all.x=TRUE) 
#rename column
colnames(OrigData)[colnames(OrigData)=="NY.GDP.PCAP.CD"] <- "EnterGDP"
# clean up- merging adds some extra country columns we do not want to keep
OrigData$country.x <- NULL
OrigData$country.y <- NULL
```
Merging World Bank Data: GDP Exityear
```{r}
# Need to rename Country to match WDI year. We now want the same information as before but for a different year.
colnames(wdi.gdp)[colnames(wdi.gdp)=="Coupyear"] <- "Exityear"
OrigData <- merge(OrigData,wdi.gdp,by=c("Exityear", "iso2c"),all.x=TRUE)
#Rename GDP category
colnames(OrigData)[colnames(OrigData)=="NY.GDP.PCAP.CD"] <- "ExitGDP"
# clean up excess columns
OrigData$country.x <- NULL
OrigData$country.y <- NULL
```
Merging World Bank Data: GDP Election Year
```{r}
# Need to create an election Year GDP 
colnames(wdi.gdp)[colnames(wdi.gdp)=="Exityear"] <- "Electionyear"
OrigData <- merge(OrigData,wdi.gdp,by=c("Electionyear", "iso2c"),all.x=TRUE)
colnames(OrigData)[colnames(OrigData)=="NY.GDP.PCAP.CD"] <- "ElectionGDP"
# clean up
OrigData$country.x <- NULL
OrigData$country.y <- NULL
```
Merging World Bank Data: GDP Two years before Election
```{r}
#First we need to create new variable that calculates what year it is two years prior to the election
OrigData$TwoYearsBElection<-NULL
OrigData$TwoYearsBElection <- (as.numeric(OrigData$Electionyear)- 2)
# Now we can merge as we have been
colnames(wdi.gdp)[colnames(wdi.gdp)=="Electionyear"] <- "TwoYearsBElection"
OrigData <- merge(OrigData,wdi.gdp,by=c( "TwoYearsBElection", "iso2c"),all.x=TRUE)
colnames(OrigData)[colnames(OrigData)=="NY.GDP.PCAP.CD"] <- "GDP2YBeforeElection"
# clean up
OrigData$country.x <- NULL
OrigData$country.y <- NULL
```

Now we can calculate the Difference in GDP
```{r}
# Change in economy during time in Power.
OrigData$ImprovGDP <- OrigData$ExitGDP-OrigData$EnterGDP
# Change in econoy prior to election
OrigData$StatusofGDP <- as.numeric(OrigData$ElectionGDP-OrigData$GDP2YBeforeElection)
```
Merging Polity Data: Loading Data
```{r}
#loading polity data - it is large so this may take a minute or two.
P4 <- read.xls("p4v2014.xls")
#Subseting to keep columns of interest, if you skip this you will merge a ton of columns that will just crowd the dataset
keepvariables <- c("country", "year", "polity", "polity2", "durable", "democ", "autoc")
P4subset <- P4[keepvariables]
# assigning cown country code
P4subset$cown <- countrycode(P4subset$country, "country.name", "cown")
```
Merging Polity Data: Coup Year
```{r}
# merging the Polity score from the beginning of the coup
colnames(P4subset)[colnames(P4subset)=="year"] <- "Coupyear"
OrigData  <- merge(OrigData,P4subset,by=c("cown", "Coupyear"),all.x=TRUE)
# rename Columns
colnames(OrigData)[colnames(OrigData)=="democ"] <- "Enterdemoc"
colnames(OrigData)[colnames(OrigData)=="autoc"] <- "Enterauto"
colnames(OrigData)[colnames(OrigData)=="polity"] <- "Enterpolity"
colnames(OrigData)[colnames(OrigData)=="polity2"] <- "Enterpolity2"
colnames(OrigData)[colnames(OrigData)=="durable"] <- "Enterdurable"
```
Merging Polity Data: Exit Year
```{r}
# merging the Polity score from the end of the coup
#I need to rename the P4 year because it needs to be able to match
colnames(P4subset)[colnames(P4subset)=="Coupyear"] <- "Exityear"
# merge end date polity scores
OrigData  <- merge(OrigData,P4subset, by=c("cown", "Exityear"),all.x=TRUE)
# Rename new polity columns 
colnames(OrigData)[colnames(OrigData)=="democ"] <- "Exitdemoc"
colnames(OrigData)[colnames(OrigData)=="autoc"] <- "Exitauto"
colnames(OrigData)[colnames(OrigData)=="polity"] <- "Exitpolity"
colnames(OrigData)[colnames(OrigData)=="polity2"] <- "Exitpolity2"
colnames(OrigData)[colnames(OrigData)=="durable"] <- "Exitdurable"
colnames(OrigData)[colnames(OrigData)=="country.x"] <- "country"
OrigData$country.y <- NULL
```
Merging Polity Data: Election Year
```{r}
#I need to rename the P4 year because it needs to be able to match
colnames(P4subset)[colnames(P4subset)=="Exityear"] <- "Electionyear"
# merge end date polity scores
OrigData  <- merge(OrigData,P4subset, by=c("cown", "Electionyear"),all.x=TRUE)
# Rename new polity columns 
colnames(OrigData)[colnames(OrigData)=="democ"] <- "Electiondemoc"
colnames(OrigData)[colnames(OrigData)=="autoc"] <- "Electionauto"
colnames(OrigData)[colnames(OrigData)=="polity"] <- "Electionpolity"
colnames(OrigData)[colnames(OrigData)=="polity2"] <- "Electionpolity2"
colnames(OrigData)[colnames(OrigData)=="durable"] <- "Electiondurable"
colnames(OrigData)[colnames(OrigData)=="country.x"] <- "country"
OrigData$country.y <- NULL
```
Calculating the Differences in Polity Scores
```{r}
# first we need to get rid of codes used to denote missing values as these would through off the differences

# Democracy Score
OrigData$Enterdemoc[OrigData$Enterdemoc==-77]<- NA
OrigData$Enterdemoc[OrigData$Enterdemoc==-88]<- NA
OrigData$Exitdemoc[OrigData$Exitdemoc==-77]<- NA
OrigData$Exitdemoc[OrigData$Exitdemoc==-88]<- NA

#Polity Score
OrigData$Enterpolity2[OrigData$Enterpolity2==-77]<- NA
OrigData$Enterpolity2[OrigData$Enterpolity2==-88]<- NA
OrigData$Exitpolity2[OrigData$Exitpolity2==-77]<- NA
OrigData$Exitpolity2[OrigData$Exitpolity2==-88]<- NA

#Polity Two Score 
OrigData$Enterpolity[OrigData$Enterpolity==-77]<- NA
OrigData$Enterpolity[OrigData$Enterpolity==-88]<- NA
OrigData$Exitpolity[OrigData$Exitpolity==-77]<- NA
OrigData$Exitpolity[OrigData$Exitpolity==-88]<- NA

# Calculating the Difference
OrigData$ImprovDemo <- OrigData$Exitdemoc - OrigData$Enterdemoc
OrigData$Improvpolity <- OrigData$Exitpolity- OrigData$Enterpolity
OrigData$Improvpolity2 <- OrigData$Exitpolity2- OrigData$Enterpolity2
```

Descriptive Statistics: Comparing Win and Lose
```{r}
sum(OrigData$Win==1, na.rm=TRUE)
sum(OrigData$Win==0, na.rm=TRUE)
```
Descriptive Statistics: Comparing Means with Box plots
```{r}
# First we want to subset the Data so we are only looking at individuals who had a successful coup. This is important because if you look at everyone you are going to get a lot of zeros as failed coup leaders and no effect on any of the measures.

OrigDatasubSuccess<- OrigData[which(OrigData$Successful==1),]
# Now Graph
ImprovPolity <- ggplot(OrigDatasubSuccess, aes(factor(OrigDatasubSuccess$Win), OrigDatasubSuccess$Improvpolity))+geom_boxplot()+ geom_jitter(colour = "black") + ylim(-10, 10) + labs(y="Improvement in Polity score During time in Power", x="Election Outcome", title="Differences in Improvement in Polity Score During time in Power")+ theme(panel.background = element_rect(fill='white', colour='black'))+ coord_flip()

ImprovPolity

ImprovDemo <-ggplot(OrigDatasubSuccess, aes(factor(OrigDatasubSuccess$Win), OrigDatasubSuccess$ImprovDemo))+geom_boxplot()+ geom_jitter(colour = "black") + ylim(-10, 10) + labs(y="Improvement in demo Polity score During time in Power", x="Election Outcome", title="Differences in Improvement in demo Polity Score During time in Power")+ theme(panel.background = element_rect(fill='white', colour='black'))+ coord_flip()
ImprovDemo

ImprovGDP <-ggplot(OrigDatasubSuccess, aes(factor(OrigDatasubSuccess$Win), OrigDatasubSuccess$ImprovGDP))+geom_boxplot()+ geom_jitter(colour = "black") + labs(y="Improvement in GDP During time in Power", x="Election Outcome", title="Differences in Improvement in GDP During time in Power")+ theme(panel.background = element_rect(fill='white', colour='black'))+ coord_flip()
ImprovGDP

Reign.Years <-ggplot(OrigDatasubSuccess, aes(factor(OrigDatasubSuccess$Win), OrigDatasubSuccess$Reign.year))+geom_boxplot()+ geom_jitter(colour = "black") + labs(y="Length of Time in Power After Coup", x="Election Outcome", title="Differences in Time in Power after Coup")+ ylim(1,40)+ theme(panel.background = element_rect(fill='white', colour='black'))+ coord_flip()
Reign.Years


ElectionGDP <- ggplot(OrigData, aes(factor(OrigData$Win), OrigData$ElectionGDP))+geom_boxplot()+ geom_jitter(colour = "black") + labs(y="GDP during Election", x="Election Outcome", title="Differences in Election GDP")+theme(panel.background = element_rect(fill='white', colour='black'))+ coord_flip()
ElectionGDP
```

Summary Statistics: Death Toll
```{r}
# Need to create subset variables that include values only when the candidate one or loss
# DeathToll
DeathTollWin <- OrigData$Death.Toll[OrigData$Win == 1]
mean(DeathTollWin, na.rm=TRUE)
#if you get rid of case with 5000 deaths
DeathTollWinminuso <- DeathTollWin[DeathTollWin <= 500]
mean(DeathTollWinminuso, na.rm=TRUE)
# Death Toll if the canidate lost
DeathTollLose <- OrigData$Death.Toll[OrigData$Win == 0]
mean(DeathTollLose,na.rm=TRUE)
TTestDeathToll <- t.test(DeathTollWinminuso, DeathTollLose, alternative="two.sided",conf.level=0.95)
TTestDeathToll
```

Summary Statistics: Improved Demo Polity Score
```{r}
# I want to only look at Demo Polity score for candidates that won.
ImprovDemoWin <- OrigData$ImprovDemo[OrigData$Win == 1] 
# I want to only look at Demo Polity score for candidates that lost.
ImprovDemoLose <- OrigData$ImprovDemo[OrigData$Win == 0]
# mean of score improved for candidates who won
mean(ImprovDemoWin, na.rm=TRUE)
# mean of score improved for candidates who lost
mean(ImprovDemoLose, na.rm=TRUE)
#ttest
TTestImprovDemoc <- t.test(ImprovDemoWin, ImprovDemoLose,alternative="two.sided",conf.level=0.95, na.rm=TRUE)
TTestImprovDemoc
```
Summary Statistics: Improved Polity Score
```{r}
# I want to only look at Demo Polity scores for candidates that won.
ImprovPolityWin <- OrigData$Improvpolity[OrigData$Win == 1]
# I want to only look at Demo Polity scores for candidates that lost.
ImprovPolityLose <- OrigData$Improvpolity[OrigData$Win == 0]
# mean of score improved for candidates who won
mean(ImprovPolityWin, na.rm=TRUE)
# mean of score improved for candidates who lost
mean(ImprovPolityLose, na.rm=TRUE)
#ttest
TTestImprovPolity <- t.test(ImprovPolityWin, ImprovPolityLose,alternative="two.sided",conf.level=0.95, na.rm=TRUE)
TTestImprovPolity
```
Summary Statistics: Improved Polity2 Scores
```{r}
# I want to only look at Polity2 score for candidates that won.
ImprovPolity2Win <- OrigData$Improvpolity2[OrigData$Win == 1]
# I want to only look at Polity2 score for candidates that lost.
ImprovPolity2Lose <- OrigData$Improvpolity2[OrigData$Win == 0]
# mean of score improved for candidates who won
mean(ImprovPolity2Win, na.rm=TRUE)
# mean of score improved for candidates who lost
mean(ImprovPolity2Lose, na.rm=TRUE)
#ttest
TTestImprovPolity2 <- t.test(ImprovPolity2Win, ImprovPolity2Lose,alternative="two.sided",conf.level=0.95, na.rm=TRUE)
TTestImprovPolity2
```

Summary Statistics: Time off
```{r}
# I want to only look at time off for candidates that won.
Timeoff.yearswin <- OrigData$TimeOff.years[OrigData$Win == 1] 
# I want to only look at time off for candidates that lost.
Timeoff.yearslose <- OrigData$TimeOff.years[OrigData$Win == 0]
# mean time off for candidates who won
mean(Timeoff.yearswin, na.rm=TRUE)
# mean oftime off for candidates who lost
mean(Timeoff.yearslose, na.rm=TRUE)
#ttest
TTestTimeoff.years <- t.test(Timeoff.yearswin, Timeoff.yearslose,alternative="two.sided",conf.level=0.95, na.rm=TRUE)
TTestTimeoff.years 
```

Descriptive Statistics: Incumbency and Opposition
```{r}
# I want to look at only incumbents.
OrigDataIncumbent<- OrigData[OrigData$Incumbent==1,]
# How Many Incumbents Candidates Won?
sum(OrigDataIncumbent$Win==1, na.rm=TRUE)

# I want to only look at opposition candidates.
OrigDataOpp <- OrigData[OrigData$Incumbent==0,]
# How many Opposition Candidates Won?
sum(OrigDataOpp$Win==1, na.rm=TRUE)

# I want to only look at candidates who came straight from the Coup
OrigDataStraightFromCoup <- OrigData[OrigData$Incumbent==3,]
sum(OrigDataStraightFromCoup$Win==1, na.rm=TRUE)


```
Smoothed Regressions: Polity Scores
```{r}
ImprovPolityLOESS <- ggplot(OrigDatasubSuccess, aes(OrigDatasubSuccess$Improvpolity, OrigDatasubSuccess$Win)) + stat_smooth(method = "loess")+ geom_jitter(colour = "black") + labs(y="Election Outcome", x="Improvement in Polity Scores", title="Improvement in Polity Score During time in Power")+ theme(panel.background = element_rect(fill='white', colour='black'))
ImprovPolityLOESS

ImprovPolity2LOESS <- ggplot(OrigDatasubSuccess, aes(OrigDatasubSuccess$Improvpolity2, OrigDatasubSuccess$Win)) + stat_smooth(method = "loess")+ geom_jitter(colour = "black") + labs(y="Election Outcome", x="Improvement in Polity Scores", title="Improvement in Polity2 Score During time in Power")+ theme(panel.background = element_rect(fill='white', colour='black'))
ImprovPolity2LOESS 

ImprovDEMOLOESS <- ggplot(OrigDatasubSuccess, aes(OrigDatasubSuccess$ImprovDemo, OrigDatasubSuccess$Win)) + stat_smooth(method = "loess")+ geom_jitter(colour = "black") + labs(y="Election Outcome", x="Improvement in  Demo Polity Scores", title="Improvement in Demo Polity Score During time in Power")+ theme(panel.background = element_rect(fill='white', colour='black'))
ImprovDEMOLOESS
```

Lets Look at Incumbency Effects
```{r}
ImprovPolityLOESSIncumbent <- ggplot(OrigDatasubSuccess, aes(OrigDatasubSuccess$Improvpolity, OrigDatasubSuccess$Win)) + stat_smooth(method = "loess")+geom_jitter(aes(colour = factor(OrigDatasubSuccess$Incumbent))) + labs(y="Election Outcome", x="Improvement in Polity Scores", title="Improvement in Polity Score During time in Power")+ theme(panel.background = element_rect(fill='white', colour='black'))+ theme(legend.position = "bottom") + theme(legend.background = element_rect(colour = "black"))+geom_vline(xintercept=0, colour= "grey")+geom_hline(yintercept=.5, colour="grey")+scale_color_manual("Incumbency Status",labels = c("Opposition", "Incumbent", "Straight From Coup"), values = c( "red","blue", "green"))
ImprovPolityLOESSIncumbent
# The color points are showing you the candidates incumbency status, the line on the Y axis is showing you if they won or lost, as the jitter spreads out the points (above is won, below is lost). The line a zero is just to help see the change between negative and positive effects.
```
Smoothed Regressions: GDP
```{r}

StatusofGDPLOESS <- ggplot(OrigData, aes(OrigData$StatusofGDP , OrigData$Win)) + stat_smooth(method = "loess")+ geom_jitter(colour = "black")+xlim(-200, 1500) + labs(y="Election Outcome", x="Difference in Election Year GDP and GDP Two Years Prior", title="Was the Economy Better During the Election?")+ theme(panel.background = element_rect(fill='white', colour='black'))

StatusofGDPLOESS

# Lets take out Nigeria - ie the only point at 1500

StatusofGDPLOESSminus0 <- ggplot(OrigData, aes(OrigData$StatusofGDP , OrigData$Win)) + stat_smooth(method = "loess")+ geom_jitter(colour = "black")+xlim(-200, 700) + labs(y="Election Outcome", x="Difference in Election Year GDP and GDP Two Years Prior", title="Was the Economy Better During the Election?")+ theme(panel.background = element_rect(fill='white', colour='black'))
StatusofGDPLOESSminus0

# Lets Look at Incumbency Effects with GDP

OrigDataIncumbent<- OrigData[OrigData$Incumbent==1,]

StatusofGDPLOESSINCUMBENT <- ggplot(OrigDataIncumbent, aes(OrigDataIncumbent$StatusofGDP , OrigDataIncumbent$Win)) + stat_smooth(method = "loess")+ geom_jitter(colour = "black")+xlim(-200, 400) + labs(y="Election Outcome For Incumbents", x="Difference in Election Year GDP and GDP Two Years Prior", title="Was the Economy Better During the Election?")+ theme(panel.background = element_rect(fill='white', colour='black'))+geom_vline(xintercept=0, colour= "grey")+geom_hline(yintercept=.5, colour="grey")
StatusofGDPLOESSINCUMBENT

OrigDataOpp<- OrigData[OrigData$Incumbent==0,]

StatusofGDPLOESSOPP <- ggplot(OrigDataOpp, aes(OrigDataOpp$StatusofGDP , OrigDataOpp$Win)) + stat_smooth(method = "loess")+ geom_point()+ geom_jitter(colour = "black")+xlim(-200, 700) + labs(y="Election Outcome For Opposition", x="Difference in Election Year GDP and GDP Two Years Prior", title="Was the Economy Better During the Election?")+ theme(panel.background = element_rect(fill='white', colour='black'))+geom_vline(xintercept=0, colour= "grey")+geom_hline(yintercept=.5, colour="grey")
StatusofGDPLOESSOPP

OrigDataInPower<- OrigData[OrigData$Incumbent==3,]
StatusofGDPLOESSinPOwer <- ggplot(OrigDataInPower, aes(OrigDataInPower$StatusofGDP , OrigDataInPower$Win)) + stat_smooth(method = "loess")+ geom_jitter(colour = "black")+xlim(-200, 300) + labs(y="Election Outcome For Leaders Straight From Coup", x="Difference in Election Year GDP and GDP Two Years Prior", title="Was the Economy Better During the Election?")+ theme(panel.background = element_rect(fill='white', colour='black'))+geom_vline(xintercept=0, colour= "grey")+geom_hline(yintercept=.5, colour="grey")
StatusofGDPLOESSinPOwer

# In this graph we will factor by the variable Incumbency. In doing so, we will hopefully be able to see a more detailed picture of the effect of GDP per varying type of candidate

StatusofGDPLOESSV2 <- ggplot(OrigData, aes(OrigData$StatusofGDP , OrigData$Win)) + stat_smooth(method = "loess")+ geom_jitter(aes(colour = factor(OrigData$Incumbent)))+xlim(-200, 1600) + labs(y="Election Outcome", x="Difference in Election Year GDP and GDP Two Years Prior", title="Was the Economy Better During the Election?")+ theme(panel.background = element_rect(fill='white', colour='black'))+ theme(legend.position = "bottom") + theme(legend.background = element_rect(colour = "black"))+geom_vline(xintercept=0, colour= "grey")+geom_hline(yintercept=.5, colour="grey")+scale_color_manual("Incumbency Status",labels = c("Opposition", "Incumbent", "Straight From Coup"), values = c("red","blue", "green"))
StatusofGDPLOESSV2
# The color points are showing you the candidates incumbency status, the line on the Y axis is showing you if they won or lost, as the jitter spreads out the points (above is won, below is lost). The line a zero is just to help see the change between negative and positive effects.

# Lets take out the problem child that is Nigeria
StatusofGDPLOESSV2minuso <- ggplot(OrigData, aes(OrigData$StatusofGDP , OrigData$Win)) + stat_smooth(method = "loess")+ geom_jitter(aes(colour = factor(OrigData$Incumbent)))+xlim(-200, 600) + labs(y="Election Outcome", x="Difference in Election Year GDP and GDP Two Years Prior", title="Was the Economy Better During the Election?")+ theme(panel.background = element_rect(fill='white', colour='black'))+ theme(legend.position = "bottom") + theme(legend.background = element_rect(colour = "black"))+geom_vline(xintercept=0, colour= "grey")+geom_hline(yintercept=.5, colour="grey")+scale_color_manual("Incumbency Status",labels = c("Opposition", "Incumbent", "Straight From Coup"), values = c( "red","blue", "green"))
StatusofGDPLOESSV2minuso
# We can also look at maj/min ethnic group in terms of election results

StatusofGDPEthnicminuso <- ggplot(OrigData, aes(OrigData$StatusofGDP , OrigData$Win)) + stat_smooth(method = "loess")+ geom_jitter(aes(colour = factor(OrigData$MajEthnic)))+xlim(-200, 600) + labs(y="Election Outcome", x="Difference in Election Year GDP and GDP Two Years Prior", title="Was the Economy Better During the Election?")+ theme(panel.background = element_rect(fill='white', colour='black'))+ theme(legend.position = "bottom") + theme(legend.background = element_rect(colour = "black"))+geom_vline(xintercept=0, colour= "grey")+geom_hline(yintercept=.5, colour="grey")+scale_color_manual("Member of Majority Ethnic Group?",labels = c("No", "Yes"), values = c( "red","blue"))
StatusofGDPEthnicminuso 

```
Smoothed Regressions: Time Off
```{r}

TimeOffReg <- ggplot(OrigData, aes(OrigData$TimeOff.year , OrigData$Win)) + stat_smooth(method = "loess")+ geom_jitter(aes(colour = factor(OrigData$Incumbent)))+xlim(0, 40) + labs(y="Election Outcome", x="Time Off From Coup To Election", title="Does the Time Between The Coup and Election Matter?")+ theme(panel.background = element_rect(fill='white', colour='black'))+ theme(legend.position = "bottom") + theme(legend.background = element_rect(colour = "black"))+geom_hline(yintercept=.5, colour="grey")+scale_color_manual("Incumbency Status",labels = c("Opposition", "Incumbent", "Straight From Coup"), values = c( "red","blue", "green"))
TimeOffReg
```
Lets Build Some Tables: Trying out Stargazer
```{r}
# first I want to subset data frame to only keep columns I want to show
OrigDataimprovsumm <- OrigData[c("ImprovDemo", "Reign.weeks", "ImprovGDP", "Improvpolity")]
stargazer(OrigDataimprovsumm, summary=TRUE)
```




